### 2022-05-17 manuscript.Rmd
Make headings comply with formatting guidelines

author:
  - name          : "Alexander Enge"
    affiliation   : "1,2"
  - name          : "Shreya Kapoor"
    affiliation   : "1"
  - name          : "Anne-Sophie Kieslinger"
    affiliation   : "1"
  - name          : "Michael A. Skeide"
    affiliation   : "1"
affiliation:
  - id            : "1"
    institution   : "Research Group Learning in Early Childhood, Max Planck Institute for Human Cognitive and Brain Sciences, Stephanstraße 1a, Leipzig, Germany"
  - id            : "2"
    institution   : "Department of Psychology, Humboldt-Universität zu Berlin, Rudower Chaussee 18, Berlin, Germany"

@@

# Introduction

@@

# Results

@@

# Discussion

@@

## Effect size estimates

@@

## Gender differences

@@

## Additional factors

@@

# Conclusion

@@

\noindent M.A.S. conceived, designed, and obtained funding for the study.

\noindent A.E., S.K., and A.-S.K. designed and executed the search and selection strategies, performed data analysis, conducted robustness checks, and visualized the results in consultation with M.A.S.

\noindent A.E. and M.A.S. wrote the manuscript with additional input from S.K. and A.-S.K.

@@

\noindent The authors declare no competing interests.

# Corresponding author

\noindent Correspondence concerning this article should be addressed to Alexander Enge, Stephanstraße 1a, 04103 Leipzig, Germany. E-mail: [enge@cbs.mpg.de](mailto:enge@cbs.mpg.de)

>>>>

author:
  - name          : "Alexander Enge"
    affiliation   : "1,2,*"
  - name          : "Shreya Kapoor"
    affiliation   : "1"
  - name          : "Anne-Sophie Kieslinger"
    affiliation   : "1"
  - name          : "Michael A. Skeide"
    affiliation   : "1"
affiliation:
  - id            : "1"
    institution   : "Research Group Learning in Early Childhood, Max Planck Institute for Human Cognitive and Brain Sciences, Stephanstraße 1a, Leipzig, Germany"
  - id            : "2"
    institution   : "Department of Psychology, Humboldt-Universität zu Berlin, Rudower Chaussee 18, Berlin, Germany"
  - id            : "*"
    institution   : "Corresponding author (enge@cbs.mpg.de)"

@@

# Main

@@

@@

## Discussion

@@

@@

@@

@@

@@

M.A.S. conceived, designed, and obtained funding for the study. A.E., S.K., and A.-S.K. (in consultation with M.A.S.) designed and executed the search and selection strategies, performed data analysis, conducted robustness checks, and visualized the results. A.E. and M.A.S. wrote the manuscript with additional input from S.K. and A.-S.K.

@@

The authors declare no competing interests.

# Additional information

Supplementary Information is available for this paper. Correspondence and requests for materials should be addressed to Alexander Enge ([enge@cbs.mpg.de](mailto:enge@cbs.mpg.de)).
